Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
Descrito el a priori enforcement. Closes #23

The client is an important part of the a-priori risk treatment, because it both monitors the whole context and finally acts or warns the user in event of a security violation. Security violations are mainly identified by security rules, which is why MUSES uses DM and CI techniques to evolve them and enhance the coverage. That is to say, the more sensors are implemented, the more enforced the security in the device is. %Esta última frase revisádmela por favor, e insultadme si es necesario.
 For this reason, MUSES implements the following sensors:

\begin{description}
  \item[CONNECTIVITY SENSOR] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours. This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough. 
  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}. This security mechanism %¿cambiarlo por "This security mechanism" ? % Ok, cambiado, creo que está mejor así.
   adds the possibility of detecting security violations even if the user is not doing a specific action.
  \item[LOCATION SENSOR] User location can be obtained from the device GPS. Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
  \item[MAIL SENSOR] If the user is going to send an email, MUSES client sensors check also the email attributes. This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
  \item[FILE SENSOR] The type of file, also called \textit{asset}, is also very important for the application of security rules. Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
  \item[APP SENSOR] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications. Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.
\end{description}

>>>>

The client is an important part of the a-priori risk treatment, because it both monitors the whole context and finally acts or warns the user in event of a security violation. Security violations are mainly identified by security rules, which is why MUSES uses DM and CI techniques to evolve them and enhance the coverage. That is to say, the more sensors are implemented, the more enforced the security in the device is. To implement a sensor means to include a programmed method which makes MUSES to start `listening' some parts of a device. 
For this reason, MUSES implements the following sensors:

\begin{description}
  \item[CONNECTIVITY SENSOR] It gathers all information related to network communications, in addition to security properties like network encryption, or number of neighbours. This allows MUSES actuator to forbid the user for sending important emails, or opening key assets if, for instance, the network encryption is not secure enough. 
  \item[DEVICE PROTECTION SENSOR] Which scans device security settings, such as the time until the device screen turns off, if the device has the screen protected with a password, or if the device is rooted \cite{hildenbrand2014}. This security mechanism adds the possibility of detecting security violations even if the user is not doing a specific action.
  \item[LOCATION SENSOR] User location can be obtained from the device GPS. Although, and to preserve user privacy, a number of `zones' can be defined by the company, so MUSES only checks if the user is inside them and acts in consequence.
  \item[MAIL SENSOR] If the user is going to send an email, MUSES client sensors check also the email attributes. This way, they can detect if the event context is dangerous, according to security policies and the RT2AE, before the mail is sent.
  \item[FILE SENSOR] The type of file, also called \textit{asset}, is also very important for the application of security rules. Thus, this sensor aims to detect is some files might need more strict security policies, also depending on the rest of sensors.
  \item[APP SENSOR] It is in charge of monitoring the information about the application from which the user is performing the action, but also looks for installed trusted antivirus, and encryption applications. Additionally, this sensor gathers information abaut the applicationes which the user tries to install or uninstall.
\end{description}
